---
title: "How to use this webpage?"
# subtitle: "Weekly Lecture Plan, Evaluation of the Class and Materials"
format: 
  live-html:
    css: webex.css
    include-after-body: webex.js
engine: knitr
link-external-icon: true
link-external-newwindow: true
---

{{< include ./_extensions/live/_knitr.qmd >}}
{{< include ./_extensions/live/_gradethis.qmd >}}

This webpage is most likely different from other lecture notes you encountered. 

* Website contains a build in R engine, that will work as long as you are connected to the Internet.
* Most of the content would work through your web browser even if you did not install R and RStudio.
* But to prohibit laziness some of the lab sessions are intently designed to be worked on your own computers.
* Throughout the course you will encounter questions like the following and will require you to solve it.


## Sample Question

* If the desired output is `8` what should come to the ______?

:::: {.panel-tabset}

#### Sample Question

```{webr}
#| exercise: ex_1
3 + ______ 
```

#### Solution to Sample Question

::: { .solution exercise="ex_1" }

```{webr}
#| exercise: ex_1
#| solution: true
3 + 5 
```

:::

```{webr}
#| exercise: ex_1
#| check: true
gradethis::grade_code()
```

::::

::: {.callout-warning}

* You will see that, this grading schema is not perfect and we will encounter some bugs throughout the process.
* If you encounter any bugs such as 
  * `you wrote a correct answer and the evaluation says it is incorrect` or  
  * `you wrote an incorrect answer and the evaluation says it is correct` or 
  * `you find a shortcut to answer a question although it should not be considered as correct` please warn the lecturer.

:::

#### Sample Question 2

```{r setup, include = FALSE}
## package and list of various exercises
library("exams2forms")
exm <- list(
  c("./exercises/sum_vector.Rmd")
)
```

```{r quiz, echo = FALSE, message = FALSE, results = "asis"}
exams2forms(exm, n = 1)
```

